---
title: Title
author: Apoorva Lal
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    self_contained: true
    theme: flatly
    highlight: tango
    code_folding: hide
    css: "/home/alal/Templates/boilerplate/lal-css.css"
    toc: true
    toc_float: false
    toc_depth: 3
    fig_width:  10
    fig_height: 8
---


<!--- For HTML renders - selection from math_shortcuts.tex --->
`r if (!knitr:::is_latex_output()) '
$\\DeclareMathOperator*{\\argmin}{argmin}$
$\\newcommand{\\var}{\\mathrm{Var}}$
$\\newcommand{\\epsi}{\\varepsilon}$
$\\newcommand{\\phii}{\\varphi}$
$\\newcommand{\\tra}{^{\\top}}$
$\\newcommand{\\sumin}{\\sum_{i=1}^n}$
$\\newcommand{\\sumiN}{\\sum_{i=1}^n}$
$\\newcommand{\\norm}[1]{\\left\\Vert{#1} \\right\\Vert}$
$\\newcommand\\Bigpar[1]{\\left( #1 \\right )}$
$\\newcommand\\Bigbr[1]{\\left[ #1 \\right ]}$
$\\newcommand\\Bigcr[1]{\\left\\{ #1 \\right \\}}$
$\\newcommand\\SetB[1]{\\left\\{ #1 \\right\\}}$
$\\newcommand\\Sett[1]{\\mathcal{#1}}$
$\\newcommand{\\Data}{\\mathcal{D}}$
$\\newcommand{\\Ubr}[2]{\\underbrace{#1}_{\\text{#2}}}$
$\\newcommand{\\Obr}[2]{ \\overbrace{#1}^{\\text{#2}}}$
$\\newcommand{\\sumiN}{\\sum_{i=1}^N}$
$\\newcommand{\\dydx}[2]{\\frac{\\partial #1}{\\partial #2}}$
$\\newcommand\\Indic[1]{\\mathds{1}_{#1}}$
$\\newcommand{\\Realm}[1]{\\mathbb{R}^{#1}}$
$\\newcommand{\\Exp}[1]{\\mathbb{E}\\left[#1\\right]}$
$\\newcommand{\\Expt}[2]{\\mathbb{E}_{#1}\\left[#2\\right]}$
$\\newcommand{\\Var}[1]{\\mathbb{V}\\left[#1\\right]}$
$\\newcommand{\\Covar}[1]{\\text{Cov}\\left[#1\\right]}$
$\\newcommand{\\Prob}[1]{\\mathbf{Pr}\\left(#1\\right)}$
$\\newcommand{\\Supp}[1]{\\text{Supp}\\left[#1\\right]}$
$\\newcommand{\\doyx}{\\Prob{Y \\, |\\,\\mathsf{do} (X = x)}}$
$\\newcommand{\\doo}[1]{\\Prob{Y |\\,\\mathsf{do} (#1) }}$
$\\newcommand{\\R}{\\mathbb{R}}$
$\\newcommand{\\Z}{\\mathbb{Z}}$
$\\newcommand{\\wh}[1]{\\widehat{#1}}$
$\\newcommand{\\wt}[1]{\\widetilde{#1}}$
$\\newcommand{\\wb}[1]{\\overline{#1}}$
$\\newcommand\\Ol[1]{\\overline{#1}}$
$\\newcommand\\Ul[1]{\\underline{#1}}$
$\\newcommand\\Str[1]{#1^{*}}$
$\\newcommand{\\F}{\\mathsf{F}}$
$\\newcommand{\\ff}{\\mathsf{f}}$
$\\newcommand{\\Cdf}[1]{\\mathbb{F}\\left(#1\\right)}$
$\\newcommand{\\Cdff}[2]{\\mathbb{F}_{#1}\\left(#2\\right)}$
$\\newcommand{\\Pdf}[1]{\\mathsf{f}\\left(#1\\right)}$
$\\newcommand{\\Pdff}[2]{\\mathsf{f}_{#1}\\left(#2\\right)}$
$\\newcommand{\\dd}{\\mathsf{d}}$
$\\newcommand\\Normal[1]{\\mathcal{N} \\left( #1 \\right )}$
$\\newcommand\\Unif[1]{\\mathsf{U} \\left[ #1 \\right ]}$
$\\newcommand\\Bern[1]{\\mathsf{Bernoulli} \\left( #1 \\right )}$
$\\newcommand\\Binom[1]{\\mathsf{Bin} \\left( #1 \\right )}$
$\\newcommand\\Pois[1]{\\mathsf{Poi} \\left( #1 \\right )}$
$\\newcommand\\BetaD[1]{\\mathsf{Beta} \\left( #1 \\right )}$
$\\newcommand\\Diri[1]{\\mathsf{Dir} \\left( #1 \\right )}$
$\\newcommand\\Gdist[1]{\\mathsf{Gamma} \\left( #1 \\right )}$
$\\def\\mbf#1{\\mathbf{#1}}$
$\\def\\mrm#1{\\mathrm{#1}}$
$\\def\\mbi#1{\\boldsymbol{#1}}$
$\\def\\ve#1{\\mbi{#1}}$
$\\def\\vee#1{\\mathbf{#1}}$
$\\newcommand{\\Mat}[1]{\\mathbf{#1}}$
$\\newcommand{\\eucN}[1]{\\norm{#1}}$
$\\newcommand{\\lzero}[1]{\\norm{#1}_0}$
$\\newcommand{\\lone}[1]{\\norm{#1}_1}$
$\\newcommand{\\ltwo}[1]{\\norm{#1}_2}$
$\\newcommand{\\pnorm}[1]{\\norm{#1}_p}$
'`


<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r}
options(digits=2)
# %% ####################################################
rm(list = ls())
library(LalRUtils)
libreq(data.table, ggplot2)
theme_set(lal_plot_theme())
options(repr.plot.width=12, repr.plot.height=9)
set.seed(42)
# %% ####################################################


knitr::opts_chunk$set(
  echo =    T,          # don't show code
  include = T,          # show output
  warning = F,       # don't show warnings
  message = F,       # don't show messages (less serious warnings)
  cache   = F,       # F unless runtime is very long
  # root.dir = 'location_of_dependencies'
  fig.align = "center"
)
```

The quick brown fox jumped over the lazy dog^[but the dog's laziness
is heavily debated].

\begin{align*}
\max_{c_t,k_{t+1}} &  \sum_{t=1}^{\infty} \beta^t u(c_t)  \\
  s.t. & \enspace c_{t} + k_{t+1} \leq f(k_t) + (1-\delta)k_t
\end{align*}

# Estimation Framework

\begin{align*}
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p
PPI_{ict-k} + \gamma_{ct} + \epsilon_{ict} \\
\text{outcome}_{ict} = \alpha_i & + \sum_{k=0}^2 \beta_{t-k}^p PPI_{ict-k} +
\sum_{k=0}^2 + \beta_{t-k}^m CPI_{ict-k} + \\ & \gamma_{c}\times
trend_t + \epsilon_{ict}
\end{align*}

# Regression output

```{r}
lm1 = felm(hwy ~ cyl ,   data = mpg)
lm2 = (felm(hwy ~ cyl | factor(trans)| 0 | manufacturer, data=mpg))
```

```{r, results='asis'}
#%%
stargazer(lm1, lm2, type='html')
#%%
```

# Figures

```{r, fig.margin=T}
#%%
library(ggplot2)
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
#%%
```

# Bibliography
