---
title: "article title"
description: |
  abstract for writeup here
author:
  - name: Apoorva Lal
    affiliation: Stanford
    url: http://apoorvalal.github.io/
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    code_download: true
    self_contained: true
backend: biber
bibliography: /home/alal/Dropbox/MyLibrary2.bib
---


<!--- For HTML renders - selection from math_shortcuts.tex --->
`r if (!knitr:::is_latex_output()) '
$\\DeclareMathOperator*{\\argmin}{argmin}$
$\\newcommand{\\var}{\\mathrm{Var}}$
$\\newcommand{\\epsi}{\\varepsilon}$
$\\newcommand{\\phii}{\\varphi}$
$\\newcommand{\\tra}{^{\\top}}$
$\\newcommand{\\sumin}{\\sum_{i=1}^n}$
$\\newcommand{\\sumiN}{\\sum_{i=1}^n}$
$\\newcommand{\\norm}[1]{\\left\\Vert{#1} \\right\\Vert}$
$\\newcommand\\Bigpar[1]{\\left( #1 \\right )}$
$\\newcommand\\Bigbr[1]{\\left[ #1 \\right ]}$
$\\newcommand\\Bigcr[1]{\\left\\{ #1 \\right \\}}$
$\\newcommand\\SetB[1]{\\left\\{ #1 \\right\\}}$
$\\newcommand\\Sett[1]{\\mathcal{#1}}$
$\\newcommand{\\Data}{\\mathcal{D}}$
$\\newcommand{\\Ubr}[2]{\\underbrace{#1}_{\\text{#2}}}$
$\\newcommand{\\Obr}[2]{ \\overbrace{#1}^{\\text{#2}}}$
$\\newcommand{\\sumiN}{\\sum_{i=1}^N}$
$\\newcommand{\\dydx}[2]{\\frac{\\partial #1}{\\partial #2}}$
$\\newcommand\\Indic[1]{\\mathds{1}_{#1}}$
$\\newcommand{\\Realm}[1]{\\mathbb{R}^{#1}}$
$\\newcommand{\\Exp}[1]{\\mathbb{E}\\left[#1\\right]}$
$\\newcommand{\\Expt}[2]{\\mathbb{E}_{#1}\\left[#2\\right]}$
$\\newcommand{\\Var}[1]{\\mathbb{V}\\left[#1\\right]}$
$\\newcommand{\\Covar}[1]{\\text{Cov}\\left[#1\\right]}$
$\\newcommand{\\Prob}[1]{\\mathbf{Pr}\\left(#1\\right)}$
$\\newcommand{\\Supp}[1]{\\text{Supp}\\left[#1\\right]}$
$\\newcommand{\\doyx}{\\Prob{Y \\, |\\,\\mathsf{do} (X = x)}}$
$\\newcommand{\\doo}[1]{\\Prob{Y |\\,\\mathsf{do} (#1) }}$
$\\newcommand{\\R}{\\mathbb{R}}$
$\\newcommand{\\Z}{\\mathbb{Z}}$
$\\newcommand{\\wh}[1]{\\widehat{#1}} % Wide hat$
$\\newcommand{\\wt}[1]{\\widetilde{#1}} % Wide tilde$
$\\newcommand{\\wb}[1]{\\overline{#1}} % Wide bar$
$\\newcommand\\Ol[1]{\\overline{#1}}$
$\\newcommand\\Ul[1]{\\underline{#1}}$
$\\newcommand\\Str[1]{#1^{*}}$
$\\newcommand{\\F}{\\mathsf{F}}$
$\\newcommand{\\ff}{\\mathsf{f}}$
$\\newcommand{\\Cdf}[1]{\\mathbb{F}\\left(#1\\right)}$
$\\newcommand{\\Cdff}[2]{\\mathbb{F}_{#1}\\left(#2\\right)}$
$\\newcommand{\\Pdf}[1]{\\mathsf{f}\\left(#1\\right)}$
$\\newcommand{\\Pdff}[2]{\\mathsf{f}_{#1}\\left(#2\\right)}$
$\\newcommand{\\dd}{\\mathsf{d}}$
$\\newcommand\\Normal[1]{\\mathcal{N} \\left( #1 \\right )}$
$\\newcommand\\Unif[1]{\\mathsf{U} \\left[ #1 \\right ]}$
$\\newcommand\\Bern[1]{\\mathsf{Bernoulli} \\left( #1 \\right )}$
$\\newcommand\\Binom[1]{\\mathsf{Bin} \\left( #1 \\right )}$
$\\newcommand\\Pois[1]{\\mathsf{Poi} \\left( #1 \\right )}$
$\\newcommand\\BetaD[1]{\\mathsf{Beta} \\left( #1 \\right )}$
$\\newcommand\\Diri[1]{\\mathsf{Dir} \\left( #1 \\right )}$
$\\newcommand\\Gdist[1]{\\mathsf{Gamma} \\left( #1 \\right )}$
$\\def\\mbf#1{\\mathbf{#1}}$
$\\def\\mrm#1{\\mathrm{#1}}$
$\\def\\mbi#1{\\boldsymbol{#1}}$
$\\def\\ve#1{\\mbi{#1}} % Vector notation$
$\\def\\vee#1{\\mathbf{#1}} % Vector notation$
$\\newcommand{\\Mat}[1]{\\mathbf{#1}}$
$\\newcommand{\\eucN}[1]{\\norm{#1}}$
$\\newcommand{\\lzero}[1]{\\norm{#1}_0}$
$\\newcommand{\\lone}[1]{\\norm{#1}_1}$
$\\newcommand{\\ltwo}[1]{\\norm{#1}_2}$
$\\newcommand{\\pnorm}[1]{\\norm{#1}_p}$
'`


<!--
########     ###    ########  ######## ########
##     ##   ## ##   ##     ## ##       ##     ##
##     ##  ##   ##  ##     ## ##       ##     ##
########  ##     ## ########  ######   ########
##        ######### ##        ##       ##   ##
##        ##     ## ##        ##       ##    ##
##        ##     ## ##        ######## ##     ##
-->

```{r global_options, include=FALSE}
# %% ####################################################
rm(list = ls())
library(LalRUtils)
LalRUtils::libreq(tidyverse, data.table, stargazer2, knitr, kableExtra,
  rmarkdown, patchwork, rio, foreach, magrittr, janitor)
theme_set(lal_plot_theme())
options(repr.plot.width=12, repr.plot.height=9)
options(ggplot2.discrete.fill = RColorBrewer::brewer.pal(9, "Set1"))
options(ggplot2.discrete.colour = RColorBrewer::brewer.pal(9, "Set1"))
options(ggplot2.continuous.fill = "viridis"); options(ggplot2.continuous.colour = "viridis")
set.seed(42)
knitr::opts_chunk$set(fig.width=12, fig.height=8,
 cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE)
# %% ####################################################
```

# Introduction

@leamer1983let


$\Exp{Y | \vee{X} = \ve{x}}$


Let
$$
x = \SetB{1, \dots, 10}
$$

```{r}
x = 1:10
x
```

The quick brown fox jumped over the lazy dog.

<aside>
the dog's laziness is a stereotype.
</aside>

# Figures
```{r, layout="l-body-outset", fig.width=6, fig.height=1.5}
library(ggplot2)
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
 facet_grid(~ cut)
```

<aside>
```{r}
ggplot(mtcars, aes(hp, mpg)) + geom_point() + geom_smooth()
```

</aside>
# Tables
```{r, layout="l-body-outset"}
paged_table(mtcars)
```

# Widgets
```{r}
libreq(leaflet)
leaflet() %>%
 addTiles() %>% # Add default OpenStreetMap map tiles
 addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
```

```{r, layout="l-page", fig.height=3}
libreq(dygraphs)
dygraph(ldeaths)
```
