---
title: Presentation Topic
author: Apoorva Lal
date: \today
institute: Stanford
bibliography: /home/alal/Dropbox/MyLibrary2.bib
biblio-style: authoryear
toc: true
theme: metropolis
# themeoptions: "background=dark"
classoption: "aspectratio=169"
mainfont: IBM Plex Sans Condensed
urlcolor: blue
output:
  binb::metropolis:
    citation_package: biblatex
    keep_tex: true
    fig_width: 8
    fig_height: 7
    fig_caption: true
    df_print: kable
    dev: cairo_pdf
    latex_engine: xelatex
header-includes:
  - \definecolor{cardinal}{RGB}{140,21,21}
  - \setbeamercolor{frametitle}{bg=cardinal}
  # - \definecolor{mLightBrown}{HTML}{EB811B}
  # - \definecolor{mLightGreen}{HTML}{14B03D}
  # - \setbeamercolor{block body}{bg=mDarkTeal!30}
  # - \setbeamercolor{frametitle}{bg=mLightBrown}
---

```{r, echo=FALSE, include=FALSE}
# %% ####################################################
rm(list = ls())
library(LalRUtils)
LalRUtils::libreq(tidyverse, data.table,
  rio, magrittr, janitor, knitr, rmarkdown)
theme_set(lal_plot_theme())

options(repr.plot.width=12, repr.plot.height=9)
options(ggplot2.discrete.fill = RColorBrewer::brewer.pal(9, "Set2"))
options(ggplot2.discrete.colour = RColorBrewer::brewer.pal(9, "Set2"))
options(ggplot2.continuous.fill = "viridis"); options(ggplot2.continuous.colour = "viridis")

set.seed(42)
# %% ####################################################

opts_chunk$set(echo=F, autodep=TRUE, cache.comments=FALSE,
               message=FALSE, warning=FALSE)
```

# Scratch

## Title here

\parencite{leamer1983let}


\scriptsize cite but don't read

## Another slide

The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.

$$
y = \beta_0 + \vee{x}_i' \ve{\beta} + \epsi_i
$$

Hello, world!

## Mathy slide

\metroset{block=fill}
\begin{alertblock}{AIPW Estimator}
$$
\wh{\tau}_{\text{ipw}}^{\text{ate}} = \ooN \sumin \Bigpar{
  \underbrace{\frac{Y_iD_i}{\hat{\pi}(\Vect{X}_i)}}_{\Exp{Y_1}} -
  \underbrace{\frac{Y(1 - D_i)}{(1 - \hat{\pi}(\Vect{X}_i))}}_{\Exp{Y_0}}}
= \ooN \sumin Y_i \Bigpar{\frac{D_i}{\wh{\pi}(\ve{X}_i)} - \frac{1 -
D_i}{1 - \wh{\pi} (\ve{X}_i)}}
$$

\end{alertblock}

Places highest weight for observations with $\wh{\pi} \approx 0.5$



# Core Presentation Ingredients

## Figure from R

```{r figscatter}
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point()
```


## R Table Example

A simple `knitr::kable` example:

```{r kableEx}
knitr::kable(mtcars[1:5, 1:8],
             caption="(Parts of) the mtcars dataset")
```

## Animation

::: incremental

- this
- Now this
- And now this
:::

## Two Columns


\begin{columns}
\begin{column}{0.5\textwidth}

  \bi
    \item eh?
    \item bleh
  \ei

\end{column}
\begin{column}{0.5\textwidth}
    \begin{center}
     \includegraphics[width=1\textwidth]{covid/viz/carpet_plot_xc.png}
     \end{center}
\end{column}
\end{columns}
